Supporting Information

### 2018-03-06 SupportingInformation.Rmd
done for now implementing asymetry of tail dependence stuff for C/N data, though there are a couple small things to work out still

corlmcoru_d<-unname(corstats_d[1]-corstats_d[length(corstats_d)])
corlmcoru_K<-corstats_K[,1]-corstats_K[,numsurrog]
corlmcoru_frac_K<-sum(corlmcoru_K<corlmcoru_d)
corstats_K<-apply(FUN=quantile,X=corstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

corlmcoru_S<-corstats_S[,1]-corstats_S[,numsurrog]
corlmcoru_frac_S<-sum(corlmcoru_S<corlmcoru_d)
corstats_S<-apply(FUN=quantile,X=corstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

PlmPu_d<-unname(Pstats_d[1]-Pstats_d[length(Pstats_d)])
PlmPu_K<-Pstats_K[,1]-Pstats_K[,numsurrog]
PlmPu_frac_K<-sum(PlmPu_K<PlmPu_d)
Pstats_K<-apply(FUN=quantile,X=Pstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

PlmPu_S<-Pstats_S[,1]-Pstats_S[,numsurrog]
PlmPu_frac_S<-sum(PlmPu_S<PlmPu_d)
Pstats_S<-apply(FUN=quantile,X=Pstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

D2lmD2u_d<-D2stats_d[1]-D2stats_d[length(D2stats_d)]
D2lmD2u_K<-D2stats_K[,1]-D2stats_K[,numsurrog]
D2lmD2u_frac_K<-sum(D2lmD2u_K<D2lmD2u_d)
D2stats_K<-apply(FUN=quantile,X=D2stats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

D2lmD2u_S<-D2stats_S[,1]-D2stats_S[,numsurrog]
D2lmD2u_frac_S<-sum(D2lmD2u_S<D2lmD2u_d)
D2stats_S<-apply(FUN=quantile,X=D2stats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))
```

@@

<!--Now save a second plot to the results folder, this one about asymmetry of tail dependence-->
```{r plot_soilCN_graphic_approach_2, echo=F}
#plotting layout, units inches
xht<-0.5
ywd<-0.5
titleht<-.25
panht<-1.25
panwd<-3
gap<-.05
totwd<-2*ywd+2*panwd+2*gap
totht<-3*xht+3*panht+3*gap+titleht
pdf(file="./Results/stat_results/stat_soilCN//CNdata_AsymmTailDep.pdf",width=totwd,height=totht)

#kendall, cor
par(fig=c(ywd/totwd,
          (ywd+panwd)/totwd,
          (3*xht+2*panht+2*gap)/totht,
          (3*xht+3*panht+2*gap)/totht),
    mai=c(0,0,0,0),mgp=c(3,.15,0),tcl=-.25)
hist(corlmcoru_K,50)
points(corlmcoru_d,0,col='red')
mtext(side=3,line=0,text="Kendall-preserving surrogates")
mtext(side=1,line=1,text="Partial correlation")
#text(xlimits[1],ylimits_cor[1],labels='A',cex=1.5,adj=c(.5,0))
fracplot<-function(fracs,ylims)
{
  for (counter in 1:length(fracs))
  {
    ptxt<-''
    if (fracs[counter]>.975*numsurrog)
    {
      ptxt<-paste(">",fracs[counter],sep='')
    } 
    if (fracs[counter]<.025*numsurrog)
    {
      ptxt<-paste("<",numsurrog-fracs[counter],sep='')
    }
    yht<-ylims[2]-.1*diff(ylims)
    text(x[counter],yht,ptxt,adj=c(0.5,.5),cex=0.5,srt=90)
  }
}
fracplot(corstats_frac_K,ylimits_cor)
vlineplot<-function(x,ylims)
{
  for (counter in 1:length(x))
  {
    lines(rep(x[counter]-(x[2]-x[1])/2,2),ylims,type='l',lty='dotted')
  }
  lines(rep(x[length(x)]+(x[2]-x[1])/2,2),ylims,type='l',lty='dotted')
}
vlineplot(x,ylimits_cor)

>>>>

corlmcoru_d<-unname(corstats_d[1]-corstats_d[length(corstats_d)])
corlmcoru_K<-corstats_K[1,]-corstats_K[length(corstats_d),]
corlmcoru_frac_K<-sum(corlmcoru_K<corlmcoru_d)
corstats_K<-apply(FUN=quantile,X=corstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

corlmcoru_S<-corstats_S[1,]-corstats_S[length(corlmcoru_d),]
corlmcoru_frac_S<-sum(corlmcoru_S<corlmcoru_d)
corstats_S<-apply(FUN=quantile,X=corstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

PlmPu_d<-unname(Pstats_d[1]-Pstats_d[length(Pstats_d)])
PlmPu_K<-Pstats_K[1,]-Pstats_K[length(Pstats_d),]
PlmPu_frac_K<-sum(PlmPu_K<PlmPu_d)
Pstats_K<-apply(FUN=quantile,X=Pstats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

PlmPu_S<-Pstats_S[1,]-Pstats_S[length(Pstats_d),]
PlmPu_frac_S<-sum(PlmPu_S<PlmPu_d)
Pstats_S<-apply(FUN=quantile,X=Pstats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

D2umD2l_d<-D2stats_d[length(D2stats_d)]-D2stats_d[1]
D2umD2l_K<-D2stats_K[length(D2stats_d),]-D2stats_K[1,]
D2umD2l_frac_K<-sum(D2umD2l_K<D2umD2l_d)
D2stats_K<-apply(FUN=quantile,X=D2stats_K,MARGIN=1,prob=c(.005,0.25,.975,.995))

@@

D2umD2l_S<-D2stats_S[length(D2stats_d),]-D2stats_S[1,]
D2umD2l_frac_S<-sum(D2umD2l_S<D2umD2l_d)
D2stats_S<-apply(FUN=quantile,X=D2stats_S,MARGIN=1,prob=c(.005,0.25,.975,.995))
```

@@

<!--Now make a table, this one about asymmetry of tail dependence-->
```{r plot_soilCN_asymmtry_taildep, echo=F}
atdres<-data.frame(Statistic=c("Corl-Coru","Pl-Pu","D2u-D2l"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)
fractxt<-function(fracval)
{
  ptxt<-''
  if (fracval>.975*numsurrog)
  {
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<.025*numsurrog)
  {
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}
atdres[1,2]<-fractxt(corlmcoru_frac_K)
atdres[1,3]<-fractxt(corlmcoru_frac_S)
atdres[2,2]<-fractxt(PlmPu_frac_K)
atdres[2,3]<-fractxt(PlmPu_frac_S)
atdres[3,2]<-fractxt(D2umD2l_frac_K)
atdres[3,3]<-fractxt(D2umD2l_frac_S)
atdres
```
